---
title: "Milestone 4"
author: "Diego Martinez"
date: "2/27/2020"
output: bookdown::pdf_document2
bibliography: [bibliography.bib]
biblio-style: "apalike"
link_citations: false
toc: false

    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# necessary packages 

library(bookdown)
library(tinytex)
library(gt)
library(gtsummary)
library(stargazer)
library(knitr)
library(tidyverse)
library(devtools)



```

This is my pdf document for milestone 4 of Gov 1006 Final Project. Please refer to the Github repository for my entire project.^[[Github repository](https://github.com/diegomartinez1221/gov_1006_replication_relief_fatigue)] I am replicating Out of gas: quantifying fatigue in MLB relievers ^[[Replication Paper](https://www-degruyter-com.ezp-prod1.hul.harvard.edu/downloadpdf/j/jqas.2018.14.issue-2/jqas-2018-0007/jqas-2018-0007.pdf)] by Kyle Burris and Jacob Coleman. They seak to answer the question of quantifying velocity loss on MLB relief pitchers based on their usage in the preceding days [@burris_coleman_2018]. 

I also make use of @R-knitr, @R-stringr, and @knitr2015 for this milestone.


# GT Table 

```{r gt}

# generating random data

data <- data.frame(a = sample(1:100, 5, replace = TRUE), b = sample(1:100, 5, replace = TRUE), c = sample(1:100, 5, replace = TRUE)) 

# creating the gt table 

table<- data%>%
  gt()

# outputing the table.

table
```



# Regression Table

```{r regression, results="asis"}

# generating random data

data2 <- data.frame(a = sample(1:100, 10, replace = TRUE), b = sample(1:100, 10, replace = TRUE), c = sample(1:100, 10, replace = TRUE))

# making regression models for the data 

mod <- lm(data2$a ~ data2$b) 
mod2<- lm(data2$a ~ data2$c) 

# using stargazer to output the models as a regression table 

stargazer(mod, mod2, header = FALSE,
          dep.var.labels=c("a"),
          covariate.labels=c("b", "c"))
```


# References